---
title: "linear model from Web"
author: "Miguel Avila"
date: "Fall 2024"
output:
   html_document:
         toc: true
         toc_depth: 5
        
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Read about the data from the website where it is staged.  Then form three regression models; Model1 is SIMS~ARM, Model2 is SIMS~GRIP, and Model3 is SIMS~ARM+GRIP. For each model find a 95% prediction interval of SIMS given a value of 94  for GRIP and 88 for ARM. Compare Model1 with Model3 using anova. Write it up in a markdown document, push the project up to your github account and submit it back to canvas as link. 

 


```{r include=FALSE}
require(tidyverse)
require(tigerstats)
require(rgl)
require(knitr)

```

```{r}
data <- read.csv(file="https://onlinestatbook.com/case_studies_rvls/physical_strength/data.txt",sep="",header=TRUE)  

```

## Model 1 SIM~ARMS

### scatterplot

```{r}
plot(SIMS~ARM,data=data)
model.1=lm(SIMS~ARM,data=data)
abline(model.1)
```

This scatterplot shows that simulated strength increases with the increase in arm strenth.

### Numerical results

```{r}
cor(SIMS~ARM,data=data)
```

The numerical correlation = 0.69 shows moderate positive correlation between sim score and arm strength.

### Inferential  (Build model.1)

```{r}
summary.lm(model.1)
```

The model.1 shows that the intercept and coefficient of ARM are both significantly different from 0.05


#### Predict at target point

```{r}
targtPoint = data.frame(GRIP=94, ARM=88)
predictInt = predict(model.1, targtPoint, interval = 'prediction')
print(predictInt)
```

At ARM=88, GRIP=94, the predicted SIMS score is 0.71. 95% confidence interval for that score is SIMS between -1.73 and 3.14


#### scatterplot with model fit
  

## Model 2 SIM~GRIP

### Now add in scatterplot

```{r}
plot(SIMS~GRIP,data=data)
model.2=lm(SIMS~ARM,data=data)
abline(model.2)
```

This scatterplot shows that simulated strength increases with the increase in grip strength.

### Numerical results 
```{r}
cor(SIMS~GRIP,data=data)
```

The numerical correlation = 0.64 shows moderate positive correlation between sim score and grip strength.

### Inferential  (Build model.2)
  
```{r}
summary.lm(model.2)
```

The model.2 shows that the intercept and coefficient of GRIP are both significantly different from 0.05


#### predict model.2 at target point

```{r}
targtPoint = data.frame(GRIP=94, ARM=88)
predictInt = predict(model.2, targtPoint, interval = 'prediction')
print(predictInt)
```

At ARM=88, GRIP=94, the predicted SIMS score is 0.71. 95% confidence interval for that score is SIMS between -1.73 and 3.14   

#### now add the model fit to our plot for model.2
  


## Model 3 SIM~ARM+GRIP

### Numerical results (cor)

```{r}
cor(SIMS~ARM+GRIP,data=data)
```
The numerical shows that the correlation = 0.74 shows that there is a moderate positive correlation between simulated strentgth scores and grip strength.
  
### Inferential  (Build 2-dimentional model.3)

```{r}
summary.lm(model.2)
```


#### predict model.3 at target point
  

## Comparing nested models ANOVA Test

### Model.1 vs Model.3
### Model.2 vs Model.3

## Informally compare Model.1 with model.2

